The semantic drift of quotations in blogspace: a case study in short-term cultural evolution

### 2016-08-20 reviews/2016-07-response-to-reviewers.tex

}

\answerok{
We acknowledge these issues and worked extensively to address them.  In particular (further details may also be found in the responses to reviewers): 
\itx{
\x We developed a variety of substitution models to show that the results are robust
\x We rationalized feature selection, adding some variables and much detail to this section
\x In general, we clarified further the assumptions we made, such as the restriction to single substitutions
\x We also introduced manually-coded precision \& recall analyses for all filters, which justifies our choices.
}
}

\critique{
2. The conclusions about “contractile” processes seem pretty speculative (as almost all reviewers agreed).   Sure, this might be the theoretical implication of iterating this substitution process, but you do not present any further evidence of this type of contraction towards a fixed point.  I think if you want to make this a major conclusion of the paper there is more work to be done.  Also this idea has been explored, in my view, in a much more sophisticated way in the iterated learning literature (e.g., Kalish, Lewandowsky, Griffiths, Kirby… see my PDF comments for specific references).  You should really check these arguments and papers out because you really have an iterated learning task.
}

\answerok{We agree that the initial manuscript overstated some results. We believe the new manuscript states its claims more appropriately, and makes a better distinction between actual conclusions and open questions that could not be addressed given the data (in particular, we attempted to explore substitution chains in earlier stages of this work, but were quickly limited by the constraints of the data).

We \tb{had also overlooked} several developments in the iterated learning literature, and are grateful for the \tb{various} pointers. The works we thought were most relevant have been integrated to the introductory sections, and their implications for our work are discussed in the new ``Discussion'' section.
}

@@

\answerok{We have been careful to introduce many more connections to the relevant literature: the introduction has been entirely rewritten and is followed by a more thorough presentation of the related work in cognitive science, while the concluding sections (discussion \& concluding remarks) follow your recommendation of connecting our results with the literature.
}

\critique{
Starting with the grounding, the Introduction talks about theories of "knowledge transmission mechanisms" but doesn't provide examples aside from the quote-copying problem. The theories also don't re-appear in the results discussion, leaving the experimental results stranded and unconnected to any larger domain.  No discussion of sentence recall tasks within psycholinguistics is given - there isn't a huge literature on this, but there are at least a few papers that should inform this work, such as Potter \& Lombardi 1990 "Regeneration in the short-term recall of sentences". No discussion is made about whether and how much the substitutions change the quotes (e.g., is the substituted word a synonym, phonological-neighbor, or something else? - cf. Lauf et al 2013 "Analyzing Variation Patterns in Quotes Over Time"). Lastly, the meaning of the analysis (pg. 17-19) of this process as a dynamical system with "cultural attractors" is not fleshed out - why doesn't this predict that all quotes will eventually, through substitution, converge to the same string? (Does it?) As a result, the conclusion that psycholinguistic factors don't have a big impact on substitution likelihood is interesting but doesn't have clear theoretical repercussions, or any clear meaning outside the very specific problem of quote replication.  This needs to be substantially revised and expanded to make this work useful to the audience at large.
}

\answerok{We thoroughly reworked the general grounding and flow of the manuscript. In particular:
\itx{
\x \tb{We believe that} the introductory parts provide a clearer presentation of our question and how it relates to existing literature (including the areas we overlooked) and hypotheses
\x The new ``Discussion'' section, which was indeed missing, \tb{should} properly reconnect our results to the related works introduced at the beginning of the paper.
}

Finally, several modifications in the ``Results'' section (more examples, a short discussion of the distance traveled by substitutions on the synonym network in footnote \#16, and the addition of the second null hypothesis $\mathcal{H}_{00}$ in the ``Variation'' subsection) should better describe the type of changes undergone by quotes.
}

@@

\critique{ The experiment design also has some substantial flaws. First, some crucial factors were not considered - most notably, part of speech. I suspect, for instance, that pronouns and other closed-class words are less often substituted than open-class words.  Phonological neighborhood density could also be important, though probably less so.  Second, no analysis was done that included all of the factors in, e.g., a multi-feature regression model.  While the features being considered are not strongly correlated, they are still likely to interact - especially if part-of-speech is added.  Third, the restriction to single-word substitutions introduces some significant confounds.  I'm not convinced that correctly and incorrectly copying a quote should be viewed as separate behaviors.
}

\answerok{
We addressed all these points in the revised version:
\itx{
\x We checked and discussed the susceptibility of part-of-speech (POS). While the open-/closed-class question is \tb{largely} precluded by our exclusion of stopwords from the analysis (which led us to not discuss that point in the manuscript), if we note that the manuscript's \tb{\emph{Stopword-like}} category is mainly made of \tb{closed-class words}, the data indicates that they are indeed less substituted than open-class words. As the manuscript discusses however, this concerns less than 7\% of the substitutions we consider, and has likely no effect on our results.
\x Following this suggestion, we added phonological neighborhood density as a word feature. We show that it forms a subgroup of strongly correlated variables, together with orthographic neighborhood density, and choose the latter as a more natural representative of this subgroup given the task studied.
\x We introduced a multi-feature regression model to estimate variation upon substitution, showing that the magnitude of the variation of a feature is mainly predicted by the {start word's value for} that very feature, generally with negligible interaction with the other features (see also below and figure 8).
\x We expanded substitution models to {also detect quotes undergoing up to two substitutions}, which yielded the same results as single substitutions {(see below)}. 
}

%We also examined the effect of part-of-speech (POS): Figure 5 details the results on five POS categories. A Goodman-based multinomial goodness-of-fit shows that POS categories do not capture any significant bias in the selection of substitution targets, which is why we largely keep them outside of our analysis.
}

@@

\critique{But more importantly, the $\sigma_\phi(f)$ calculation can be misleading under the single-substitution restriction: Consider a toy case where all quotes are two words, and there is a single binary feature $F$. $p(F=1) = 3/4$, and the true substitution probabilities, given the value of F, are $p(S|F=1)=1$, $p(S|F=0)=1/2$.  All the quotes where both words have feature $F=1$ will have two substitutions and be omitted from the dataset, as will half of the quotes with one $F=1$ \& one $F=0$ word.  Half of the quotes with two $F=0$ words will also be omitted for having no substitutions.  Due to these omissions, if you actually generate some test data and calculate the $\sigma_F$ values, the $\sigma_F(1)$ value is correctly estimated as 1, but the $\sigma_F(0)$ value is erroneously estimated as 1/8 (not 1/2), because the $F=0$ words are never substituted in the $F=1/F=0$ pairs, and these are three times more common than the $F=0/F=0$ pairs.  I haven't run more complicated cases, such where the length of the quotes vary, but this leads me to have limited confidence that the estimates in the Figure 4 are appropriate to draw conclusions from. I would want to see either a mathematical analysis with realistic values showing that the error is expected to be small in this data or an expansion to include multiple-substitution examples to avoid this problem.
}

\answerok{The case presented here is valid and could indeed hide a bias in our measures.
Rather than analyzing all possible such cases to bound the error, we extended substitution models to detect quotes undergoing up to two substitutions, and applied the same analysis to these mined substitutions. The results were unchanged (note: graphs produced for all models may be found at <https://huit.re/aEH77Gc3>, and may be commented further upon request). For example, the extended version of the model presented in the paper mines 70k substitutions, 9.2k of which are kept after filtering (the lowered acceptance rate indicates that more invalid substitutions are generated when allowing up to two substitutions per quote).

@@

\critique{\itx{
\x needs a substantive discussion of the results}
}

\answerok{An entirely new ``Discussion'' section is now devoted to this task.}

\critique{\itx{
\x show that the phi value is capturing what it purports to capture
\x and that the factors aren't conflated with length
\x is the single-substitution biasing the data?
\x make sure that the reported measures are interpretable
\x if low-frequency words have 1/3 chance of being chosen as substitution (Fig. 4), what if there are four low-frequency words in a quote?
}
}

\answerok{\tb{The figure 4 in the previous manuscript represented probabilities \emph{not knowing which sentence the word appears in} (i.e. marginal probabilities), which cannot be used to ask questions given a particular sentence}.

\tb{Since it appears indeed that such a measure is relatively difficult to connect to} a practical interpretation, we redefined the definition of susceptibility to make it more straightforward. \tb{We now define it relatively} to a null hypothesis\tb{: it} measures the strength of a bias \tb{affecting} a given feature value (i.e., how much a feature value is substituted compared to what it would be if targets were picked randomly). \tb{We present the corresponding results} in Figs. 5 \& 6.

Finally, we also extended our measures to capture part of the \tb{sentence-level context in which substitutions occur} (see the ``Sentence context'' subsection). Sentence-relative susceptibility, in particular, gives a straightforward answer to the question of which words are more likely to attract substitution \tb{with}in a given sentence.
}

@@

\critique{\itx{
\x improving statements of motivation and grounding within cognitive science
\x what are representation transformation processes?
\x give examples in the introduction
\x show how the quotation test case connects to more general representation transformation?}
}

\answerok{
These points should be addressed by the improved introduction. In particular regarding the last question, the new ``Discussion'' section additionally makes a connection with the iterated learning literature.
}

\critique{\itx{
\x what about the semantics of quote replication?
\x does part of speech influence substitution rate?
\x can you quantify the semantic distance between the original and substituted quote (e.g., get Mechanical Turkers to rate the semantic distance?)}
}

\answerok{We added a short discussion on the semantics of substituted quotes. We first aimed at quantifying the semantic distance by estimating the distance ``traveled'' by the substituted word in the WordNet hypernym-hyponym network as well as the FA network. This showed that substituted and substituting words are rarely direct synonyms, yet they usually achieve a similar meaning in the context of their sentence.
To further grasp the relationship of substitutions to synonyms we introduced a second null hypothesis in the ``Variation'' section, which compares the actual variation to what would happen if a random synonym of the start word was picked instead.

Finally, we also examined the effect of part-of-speech (POS): Fig. 5 details the results on five POS categories, and the subsequent discussion shows that \tb{POS categories do not capture any significant bias} in the selection of substitution targets, which is why we largely keep them outside of our analysis.
}

@@

\critique{\itx{
\x what happens when you run a multi-factor regression model? Do the features interact?
}}

\answerok{Thank you for this question. We introduced a simple regression model to check for feature interactions, which is presented in Fig. 8 with a corresponding discussion (in a nutshell: we show that features generally do not interact).}

@@

\critique{\itx{
\x clarify from the beginning the predictions you are making so that the results will be interpretable 
}}

\answerok{We hope the improved introduction is clearer as to what we \tb{expect} and what is left open due to the exploratory nature of our study.}

@@

\answerok{Except for word frequency, we observed that synonyms and phonemes were the only two word features to exhibit an effect on susceptibility (and a quite similar effect for that matter). We thus reasoned that they might exhibit a joint effect.

However, the revised version now features a much broader framework to statistically assess joint effects (see Fig. 8); we think it favorably replaces the previous variable-to-variable correlation check. (Note: we also replaced the number of phonemes with the number of letters -- which makes more sense in our context, see the end of the ``Word-level features'' subsection --, which does not seem to interact with number of synonyms).}

\critique{\itx{
\x how are you binning the continuous-valued features into categorical features for Fig 4 \& 5?
\x are there multiple y=x crossovers in Fig 5 if more bins are used?}
}

\answerok{Data in Figs. 4 \& 5 was binned into 5 integer-based bins, and the graphs were cropped whenever \tb{the data was unreasonably scarce and, accordingly,} confidence intervals were unreasonably large (which gave the impression of some graphs having only 4 bins).

\tb{Notwithstanding,} data in the new Figs. 6, 7 \& 9 is now binned into 4 quartile-based bins, which makes more sense for the confidence intervals. This decision was reached after exploring several other binning configurations: none of these substantially changed the results, but opting for quartile-based bins does improve the overall readability. Notably, no multiple crossovers were ever observed.
}

@@

\critique{ This leads into a larger issue: there is no direct word-word semantic similarity score included in the psycholinguistic variables in the analysis. Global measures such as clustering coefficients based on free association norms are included, but this isn't as appropriate, since as the authors find, the vast majority of words that are being substituted are low frequency words. Low frequency words are not as well represented in the Nelson norms, given that they are less likely to be produced, and are thus less likely to have an appropriate clustering coefficient from this dataset. Variables based on corpus analyses need to be included to provide an appropriate overview of the impacts of semantics on this task. Even so, I would suspect that global semantic network measures are not nearly as important as word-word metrics.

I would guess that the substitutions that are made in quotations are overwhelmingly higher frequency, highly semantically similar words. As the example on pg. 19 states, the substitution was "world" for "globe," where a higher frequency word replaced a lower frequency, semantically related word. There are a number of different models that can be used to assess this type of similarity, with the classic model being latent semantic analysis (Landauer \& Dumais, 1997). There are a number of additional models that have been proposed, such as Topics (Griffiths, Steyvers, \& Tenenbaum, 2007, Psyc Review) or Beagle (Jones \& Mewhort, 2007, Psyc Review). These models differ in their implementational complexity, but there are tools available that allow for useful statistics to be acquired easily. A tool by Recchia \& Jones (2010, BRM) allows for pointwise mutual information (PMI) of different words to be retrieved from a given corpus very simply. A tool such as this would allow for word-word similarity to be included in the analysis.}

\answerok{The rewritten introductory sections of this revision now \tb{aim at explaining} why we chose to use a feature-based analysis over the prediction of individual words (see below for more details about this).
Word-word similarity is now also shortly discussed in the beginning of the ``Results'' section (\tb{footnote \#15}). We explored a number of other similarity measures provided by WordNet (based on paths in the WordNet network, or on similarity of Information Content extracted from external corpora), but none of them provided more insight than what is being discussed in that section.

Finally, we introduced a new null hypothesis ($\mathcal{H}_{00}$) in the ``Variation'' subsection, which gives insight into how an appearing word relates to the synonyms of the word it replaces. \tb{While we understand that the analysis we present differs from typical approaches usually taken for similar laboratory data, we hope that these various additions contribute to alleviate concerns regarding word-word similarity.}
}

@@

\critique{I understand that word-word metrics are not easily introduced in the type of analysis that the authors are attempting to do, where the analysis of the contributions of different global psycholinguistic variables are being weighed against each other. I just think that type of analysis is inappropriate here. Since the quotations were selected on the basis of single substitutions, it seems to me that the appropriate level of analysis is what properties of the word that is being substituted is the most predictive of the substitution. I suspect that the combination of frequency and semantic similarity will be by far the most predictive variables, consistent with past results on recall.
}

\answer{We agree that predicting the actual disappearing and appearing words would be an extremely interesting result, \tb{yet we believe that this prospect stands} several steps away from what is currently possible.
\tb{As the revised introductory parts now allude to, the prediction of word intrusions is well mastered in the case of manually designed word lists but is not as exact in the case of random lists of words. Zaromb et al. (2006), for instance, predict the list from which prior-list intrusions come, but not the exact intruding word. To our knowledge, the prediction of intrusions in full sentences (either manually designed or not) has not been tackled. Finally, as explained in footnote \#4 and the ``Discussion'' section, our data set is ill-shaped to measure the accuracy of predictions we could make.
}}

@@

\critique{Beyond this, I think the authors are missing out on the most interesting aspect of the data that they have collected: how the surrounding context of the quotation used is changing across time. That is, the quote is being propagated, and the prior usage of that quote is likely predictive of how that information is spread. This is likely a dynamical process where multiple news sources are used to construct a new blog post, and being able to analyze this type of information propagation would be a very interesting study. I point to the semantic space models cited (and the work derived from them) as being very useful tools to analyze this type of question.
}

\answerok{This would indeed be a very interesting project and prospect, but the data we collected do not enable the study of the surrounding context (in particular, we know neither the prior usage nor the way information sources may be used) so that this goal remains beyond the scope of our paper.

@@

\answerok{There are indeed very many possible models, yet we agree that a robustness check is also very sensible.  Substitution detection relies on a number of assumptions and we identified four binary parameters that differentiate potential models, such that the resulting 16 combinations cover most of the reasonable answers to inference uncertainties. We thus implemented, tested and checked these models, and we can report that our results remain valid for all 16 models (for the sake of clarity, we do not specifically report on these models, though).  \\

This leads to a much more detailed ``Substitution Model'' subsection which discusses these options along with the reference model we used throughout the paper.
}

\critique{ A second issue is the time spent on feature selection.  It is unclear why the authors do feature selection at all, as "the analysis is done on a per-feature basis."  It would again add to the robustness of their claims if they showed that all of the correlated features show the same pattern of susceptibility and bias in substitution.  In the same vein, it is not clear why the authors claim that age of acquisition, frequency, and number of synonyms have low levels of correlation "excluding the network properties".  Why would one ignore the correlations with the network features?
}

\answerok{\tb{Our feature selection step aims at making} the results more intelligible. This section was indeed poorly written, and has been thoroughly revised to rationalize the process. \tb{In particular, we identify (six) groups of strongly correlated features (both manually by visual inspection and automatically with the help of an agglomeration algorithm, yielding identical results) and justify the choice of our six prototype features for each group.  Features belonging to the same group generally} exhibit very similar behaviors across all measures \tb{(with few exceptions, notably number of phonemes and number of syllables less biased than number of letters)}. Graphs produced for all features may be found at <https://huit.re/aEH77Gc3>, and could be included in a Supplementary Information bundle if requested.
}

@@

\critique{
One smaller issue has to do with the filtering of the quotations.  The authors manually inspected the filtered quotes to see how many real event-related utterances are incorrectly filtered, but I would argue the precision of the filter is more important than the recall; how many of the kept quotes are not real event-related utterances?  Why not do manual coding of those and report that accuracy?
}

\answerok{This is an important empirical point which we did not address systematically in the first submission.  We have now done this manual coding step, and improved filters wherever precision or recall were not good enough. \tb{We now assess filtering accuracy systematically and it is} satisfying in the relevant cases.}

@@

\critique{Overall, the analysis of the patterns of substitution in a series of quotations to validate psycholinguistic theory is novel and advances the current science.  The results would be more solid with some additional robustness checks, but in general they are quite intuitive.  I hope in the future the authors find a dataset that provides certain information about the transmission of language from one person to another, as this would allow for stronger claims about causality and greater confidence in the pattern of substitutions, as well as a finer-grained analysis of repeated substitutions.
}

\answerok{On a side note, we entirely agree with the relevance of pursuing this research program in these directions, as the \emph{in vitro} observation of information transmission and its evolution is part of an ongoing project (which nonetheless remains beyond the scope of the current paper).}

\subsection*{Final remarks}

### 2016-08-20 reviews/2016-07-response-to-reviewers.tex

\answerok{A few additional numbers have changed in this revised manuscript:
\itx{
\x Clustering coefficient values have changed, because Free Association link weights are now taken into account in the computation (i.e. coefficients are computed on the undirected weighted graph instead of the undirected unweighted graph).
\x An update in the language detection module led to a small change in the results of cluster filtering: there are a few more clusters and quotes than in the previous version. As a result of this, the number of words coded by Word Frequency has also changed (since frequency of words is computed from the set of quotes we keep after cluster filtering).
\x \tb{The improvement of substitution filtering}, led us to mine many more substitutions than previously. All in all \tb{raw data processing} is now much more reliable, as unit tests cover nearly all of it.
}
}
